Teaching

### 2025-08-01 research.qmd
update

As of May 2020, I am [Research Practice Lead for the University of Sheffield](https://sites.google.com/sheffield.ac.uk/orwg/research-practice). This role involves the responsibility of promoting open, transparent, robust and reproducible research at the University. Read more about [our work on open research on the Sheffield University website](https://www.sheffield.ac.uk/openresearch).

>>>>

From 2020 - 2025 I was [Research Practice Lead for the University of Sheffield](https://sites.google.com/sheffield.ac.uk/orwg/research-practice). This role involves promoting transparent, robust and reproducible research at the University. Read more about [our work on open research on the Sheffield University website](https://www.sheffield.ac.uk/openresearch).

### 2025-08-01 teaching.qmd
update

I am director for the MSc programmes in Psychological Research Methods with Data Science. I am founding director for MSc in Psychological Research Methods with Data Science. I teach a MSc module in [data management and visualisation](https://tomstafford.github.io/psy6422/).

>>>>

To 2025 I was Director for the MSc programmes in Psychological Research Methods with Data Science. I was founding director for MSc in Psychological Research Methods with Data Science. I designed and led an MSc module in [data management and visualisation](https://tomstafford.github.io/psy6422/).
